Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-12 Build_165/MDPI_submission_B165.Rmd
Commit 2023-12-13 00:18

## numeric precision
spp$slope          <- signif(spp$slope,          3)
spp$slope.p        <- signif(spp$slope.p,        3)
spp$slope.stat_sig <- signif(spp$slope.stat_sig, 3)
spp$Rsqrd          <- signif(spp$Rsqrd,          3)
spp$RsqrdAdj       <- NULL
spp$cor.t          <- NULL

>>>>

## numeric precision
spp$slope          <- signif(spp$slope,          3)
spp$slope.p        <- signif(spp$slope.p,        3)
spp$slope.stat_sig <- signif(spp$slope.stat_sig, 3)
spp$Rsqrd          <- signif(spp$Rsqrd,          3)
spp$RsqrdAdj       <- NULL
spp$cor.t          <- NULL
spp$slope.stat_sig <- NULL
